Explanatory Data Analysis of Trade Statistics of Turkey

### 2018-12-22 Draft/Draft20181218.Rmd
.

melted_data <- melted_data %>% mutate(Bins=0)
melted_data$Bins <- cut(melted_data$Ratio, breaks=c(1,10,20,30,40,50,60,70,80,90,100,1000), labels=c("1-10","11-20","21-30","31-40","41-50","51-60","61-70","71-80","81-90","91-100","100+"))
melted_data <- melted_data %>% filter((!is.na(Bins) & Bins!="1-10" &  Bins!="11-20" ) ) %>%  
  select(Country,Product_Label, year, Ratio, Bins) 
melted_data <- distinct(melted_data)

 # &  Bins!="21-30"
```

@@

  facet_wrap(~Country, scales = "free_x") +
  labs(title="Number of Products according to ImportUnitPrice/ExportUnitPrice higher than 20 times",
       y="Number of Products",
       x="Bins of Ratio of ImportUnitPrice over ExportUnitPrice") +
  theme(axis.text.x = element_text(angle=90))
```

>>>>

melted_data <- melted_data %>% mutate(Bins=0)
melted_data$Bins <- cut(melted_data$Ratio, breaks=c(1,10,20,30,40,50,60,70,80,90,100,1000), labels=c("1-10","11-20","21-30","31-40","41-50","51-60","61-70","71-80","81-90","91-100","100+"))
melted_data <- melted_data %>% filter((!is.na(Bins) & Bins!="1-10" &  Bins!="11-20" &  Bins!="21-30") ) %>%  
  select(Country,Product_Label, year, Ratio, Bins) 
melted_data <- distinct(melted_data)

 # 
```

@@

  facet_wrap(~Country, scales = "free_x") +
  labs(title="Number of Products according to ImportUnitPrice/ExportUnitPrice higher than 30 times",
       y="Number of Products",
       x="Bins of Ratio of ImportUnitPrice over ExportUnitPrice") +
  theme(axis.text.x = element_text(angle=90))
```
